\ \\ \LARGE\bf Rolling Horizon methods for Games with Continuous States and Actions

### 2014-04-02 lpaper/lunarcont.tex
one more step

  \centering
        \begin{subfigure}[b]{0.32\textwidth}
                \centering
                \includegraphics[width=1.0\textwidth]{graphics/online-IP-crop.pdf}
                \caption{Scores for a noise level of $l=1$ under variable function evaluations.\vspace{0.14in} }
                \label{fig:IP}
        \end{subfigure}   \begin{subfigure}[b]{0.32\textwidth}
                \centering
                \includegraphics[width=1.0\textwidth]{graphics/online-noise-IP_50-crop.pdf}
                \caption{Scores for 50 iterations under variable noise level $l$.}
                \label{fig:IP-N-50}
        \end{subfigure}  \begin{subfigure}[b]{0.32\textwidth}
                \centering
                \includegraphics[width=1.0\textwidth]{graphics/online-noise-IP_100-crop.pdf}
                \caption{Score for 100 iterations under variable noise level $l$.\vspace{0.14in}}
                \label{fig:IP-N-100}
        \end{subfigure}%

         \caption{Performance of all algorithms in the Inverted Pendulum benchmark (error bars for the 95th percentile). Higher scores are better}
         \label{fig:IP-all}

@@

>>>>

  \centering
        \begin{subfigure}[b]{0.32\textwidth}
                \centering
                \includegraphics[width=1.0\textwidth]{graphics/online-IP-crop.pdf}
                \caption{Scores for a noise level of $l=1$ under variable function evaluations. }
                \label{fig:IP}
        \end{subfigure}   \begin{subfigure}[b]{0.32\textwidth}
                \centering
                \includegraphics[width=1.0\textwidth]{graphics/online-noise-IP_50-crop.pdf}
                \caption{Scores for 50 iterations under variable noise level $l$.}
                \label{fig:IP-N-50}
        \end{subfigure}  \begin{subfigure}[b]{0.32\textwidth}
                \centering
                \includegraphics[width=1.0\textwidth]{graphics/online-noise-IP_100-crop.pdf}
                \caption{Score for 100 iterations under variable noise level $l$.}
                \label{fig:IP-N-100}
        \end{subfigure}%

         \caption{Performance of both T-HOLOP and EVO-P in the Inverted Pendulum benchmark (error bars for the 95th percentile). Higher scores are better}
         \label{fig:IP-all}

@@

  \centering
        \begin{subfigure}{0.49\textwidth}
                \centering
                \includegraphics[width=1.0\textwidth]{./lunarexps/sample-crop.pdf}
                \caption{Best value for each tick EVO-P could find. }
                \label{fig:sample}
        \end{subfigure}  
        \begin{subfigure}{0.49\textwidth}
                \centering
                \includegraphics[width=1.0\textwidth]{./lunarexps/sample-detail-crop.pdf}
                \caption{Detail of Figure \ref{fig:sample}, when the ship is closer to landing.}
                \label{fig:sample-detail}

        \end{subfigure}

         \caption{Sample run for EVO-P. Best fitness discovered at each tick is shown. Notice the big ``bump'' in fitness when the ship gets close to the landing pad}
         \label{fig:samples}
